A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-11-15 paper/elsarticle/elsarticle-template.tex
paper

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected.  We carry out this placement according to a small handful of steps. It is in accordance with the $X$- and $Y$-axes of the `downwards-facing' camera that we wish to place the $X$- and $Y$-axes of the augmentation; recognizing that a physical camera placed to face downwards is almost certain to not face downwards precisely, we first rotate the camera about its center of projection to align its optical axis\footnote{Strictly speaking, the optical axis is the back-projection of the principal point; in our usage, we understand it to refer to the ray through center of the image plane.} with the normal vector of the scene plane by applying the minimum arc-length rotation that relates the two, giving a \textit{virtual} camera facing directly downwards to the scene plane (cf.\ Figure~\ref{fig:virtualcam}). To obtain the virtual projector, we then (i) intersect the scene plane with the optical axis and rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and (ii) align the $X$- and $Y$-axes with those of the virtual camera. Finally, we (iii) translate along the scene plane's normal, in order to satisfy the desired metric projected image dimensions; the height $h_\text{proj}$ [m] above the ground plane at which the virtual projector is to be placed if the image---with original image width of $w_\text{im}$ [px]---is to be projected to the scene plane with a metric width of $w$ [m] is given by
\begin{equation}
h_\text{proj} = w \times f_\text{proj} / w_\text{im},
\end{equation}
where $f_\text{proj}$ [px] is the focal length of the projector. These three steps are illustrated in Figure~\ref{fig:virtualproj}. The resulting virtual projector is thus rendered fronto-parallel with the scene plane---enabling projection to the scene plane absent of projective distortions---and projects to the scene plane in the desired scale and with the the $X$- and $Y$-axes of the augmentation set in accordance with those of the `downwards-facing' camera. %\footnote{A physical camera placed to face downwards is almost certain to not face downwards precisely; in contrast, we align the virtual camera's optical axis exactly with the scene plane's normal vector, rendering it genuinely fronto-parallel with respect to the scene plane.}

@@

\begin{figure}
    \centering
    \includegraphics[height=3.75cm]{images/hans_undist_.pdf}
    \caption{Projection of warped image from Figure \ref{fig:warp}(a) to corresponding target location, acquired by the `downwards-facing' camera. Note that besides correcting for projective distortions, the warp places the axes of the augmentation in accordance with the axes of the `downwards-facing' camera, and that the dimensions of the augmentation are in line with the desired target dimensions (50~cm~$\times$~31.25~cm). To provide context, the corners of the full projected image extent are projected to the floor in light green (emphasized with overlain dashed circles).}
    \label{fig:final_proj}
\end{figure}

@@

Tables~\ref{table:length} and \ref{table:angle} give the errors in measured lengths and angles, respectively, with respect to the intended quantities. Lengths were measured using a steel rule for the top, bottom, left, and right sides of the 15~augmentations; angles were measured using a digital angle gauge at the 15~augmentations' top-left and bottom-right corners. Note that absolute errors in lengths in no instance exceeded 1~cm for any side of any of the 15~augmentations, or $1^\circ{}$ for any of the measured corners. The total amount of time expended for carrying out all the above steps amounted to ca.\ 20~min, with ca.\ 2 min going to acquisition of the camera calibration images, and ca.\ 5 min going to that of projector calibration images. The remainder of the time was spent running our modules or working with the MDC-X software. Note that once the camera is calibrated, that calibration can be reused if the camera's intrinsics remain fixed, in particular if no change is made to the zoom factor or focus settings of the camera.

>>>>

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected.  We carry out this placement according to a small handful of steps. It is in accordance with the $X$- and $Y$-axes of the `downwards-facing' camera that we wish to place the $X$- and $Y$-axes of the augmentation; recognizing that a physical camera placed to face downwards is almost certain to not face downwards precisely, we first rotate the camera about its center of projection to align its optical axis\footnote{Strictly speaking, the optical axis is the back-projection of the principal point; in our usage, we understand it to refer to the ray through center of the image plane.} with the normal vector of the scene plane by applying the minimum arc-length rotation that relates the two, giving a \textit{virtual} camera facing directly downwards to the scene plane (cf.\ Figure~\ref{fig:virtualcam}). To obtain the virtual projector, we then (i) intersect the scene plane with the optical axis and rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and (ii) align the $X$- and $Y$-axes with those of the virtual camera. Finally, we (iii) translate along the scene plane's normal, in order to satisfy the desired metric projected image dimensions; the height $h$ [m] above the ground plane at which the virtual projector is to be placed if the image---with original image width of $w_\text{im}$ [px]---is to be projected to the scene plane with a metric width of $w$ [m] is given by
\begin{equation}
h = w \times f_\text{proj} / w_\text{im},
\end{equation}
where $f_\text{proj}$ [px] is the focal length of the projector. These three steps are illustrated in Figure~\ref{fig:virtualproj}. The resulting virtual projector is thus rendered fronto-parallel with the scene plane---enabling projection to the scene plane absent of projective distortions---and projects to the scene plane in the desired scale and with the the $X$- and $Y$-axes of the augmentation set in accordance with those of the `downwards-facing' camera. %\footnote{A physical camera placed to face downwards is almost certain to not face downwards precisely; in contrast, we align the virtual camera's optical axis exactly with the scene plane's normal vector, rendering it genuinely fronto-parallel with respect to the scene plane.}

@@

\begin{figure}
    \centering
    \includegraphics[height=3.75cm]{images/hans_undist_.pdf}
    \caption{Projection of the warped image from Figure \ref{fig:warp}(a) to corresponding target location, acquired by the `downwards-facing' camera. Note that besides correcting for projective distortions, the warp places the axes of the augmentation in accordance with the axes of the `downwards-facing' camera, and that the dimensions of the augmentation are in line with the desired target dimensions (50~cm~$\times$~31.25~cm). To provide context, the corners of the full projected image extent are projected to the floor in light green (emphasized with overlain dashed circles).}
    \label{fig:final_proj}
\end{figure}

@@

Tables~\ref{table:length} and \ref{table:angle} give the errors in measured lengths and angles, respectively, with respect to the intended quantities. Lengths were measured using a steel rule for the top, bottom, left, and right sides of the 15~augmentations; angles were measured using a digital angle gauge at the 15~augmentations' top-left and bottom-right corners. Note that absolute errors in lengths in no instance exceeded 1~cm for any side of any of the 15~augmentations, or $1^\circ{}$ for any of the measured corners. The total amount of time expended for carrying out all the above steps amounted to ca.\ 20~min, with ca.\ 2 min going to acquisition of the camera calibration images, and ca.\ 5 min going to that of projector calibration images. The remainder of the time was spent running our modules or working with the MDC-X software. Note that once the camera is calibrated, that calibration can be reused if the camera's optics remain fixed, notably if no change is made to the zoom factor or focus settings of the camera.
